k-Space Domain Parallel Transmit Pulse Design

### 2020-10-23 Manuscript_r2/Method.tex
update text with dwell 10

\par A SPINS excitation k-space trajectory \cite{malik2012tailored} (Figure \ref{fig:Target}b) with 5 mm max resolution was used for the designs. 
The SPINS trajectory comprised three segments with radii ranging between 1-0.625, 0.625-0.375, and 0.375-0 cycles/cm, respectively.
The number of polar and azimuthal rotations were 15.5/2.125, 20.66/2.833, 15.5/2.125 for each segment, respectively.
The SPINS trajectories were first designed analytically and the final gradient waveforms and excitation k-space trajectories were designed from them 
using the minimum-time gradient waveform design method \cite{lustig2008fast}, 
for a 15 {\textmu}s dwell time and subject to the scanner's gradient amplitude and slew rate constraints of 200 mT/m and 700 T/m/s, respectively (Figure \ref{fig:Target}c). 
The durations of the three segments after minimum-time gradient design were 4.174, 4.326, and 1.5 ms, respectively.
With the exception of the simulations across undersampling factors, 
all pulse designs used this 10 ms trajectory.
With this trajectory and the 64$\times$64$\times$48 design grid size, 
the dimensions of the $\bm{W}$ matrix were 16,632 RF pulse samples, 
by 196,608 target k-space locations.

@@

\subsection*{k-Space Algorithm Parameters}
To evaluate how accuracy and compute time depend on k-space-domain design parameters and parallelization,
pulse designs were done across numbers of threads (i.e., how many patches were solved simultaneously; 1 to 32), 
patch widths (1 to 16 cycles/FOV), and inclusion widths (2 to 8 cycles/FOV). 
The number of threads were varied while holding the patch width and inclusion width both at 4 cycles/FOV.
The patch width was varied while holding the number of threads at 16, and the inclusion width at 4 cycles/FOV,
and the inclusion width was varied (2, 4, 6, and 8 cycles/FOV) while holding the number of threads at 16, and the patch width at 4 and 8 cycles/FOV. 
The sizes of the $\bm{W}$ matrices were also recorded, holding patch width constant at 4 cycles/FOV and varying the inclusion width.

\subsection*{L-Curves}
To compare the tradeoff between excitation error (measured by root-mean-square error)
and integrated RF root-mean-square (RMS) amplitude for spatial and k-space domain designs,
pulse designs were repeated while varying Tikhonov regularization parameters ($\lambda$ in Equation \ref{eq:Solution}) 
over five orders of magnitude. 
The k-space domain designs were repeated four times to investigate the two main sources of error:
finite patch and inclusion widths, 
and $B_1^+$ map product interpolation when building the $\bm{S}^H\bm{S}$ matrices. 
Specifically, for each $\lambda$ a design was performed using patch and inclusion widths of four (`Patch/Inclusion Widths = 4')
with interpolated $B_1^+$ map products (`Interpolated Matrices'),
patch and inclusion widths covering the entire design grid (`Patch/Inclusion Widths = $\infty$') with interpolated $B_1^+$ map products,
patch and inclusion widths of four without $B_1^+$ map product interpolation (`Exact Matrices'; 
$B_1^+$ maps were phase-modulated to each trajectory location before Fourier transform),
and patch and inclusion widths covering the entire design grid without $B_1^+$ map product interpolation. 
Note that the last case is equivalent to the original k-space domain method of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830}.
For each design, flip angle RMSE (calculated using the spatial domain NUFFT) and root-mean-square RF amplitude were
recorded.

@@

\subsection*{Excitation k-Space Undersampling}
An important application of parallel transmission is the reduction of multidimensional pulse durations by excitation k-space undersampling.
\textcolor{blue}{To compare the spatial domain and k-space domain methods across undersampling factors,
the number of polar and azimuthal rotations in each segment of the SPINS trajectory were increased and reduced relative to the reference design described above, 
by factors of 0.5, 2, and 4. 
That is, for a reduction factor of 0.5, the number of polar and azimuthal rotations in the trajectory were doubled for each of the three segments,
and they were halved for a reduction factor of 2.
This yielded pulse durations of 20.5 ms (reduction factor 0.5), 5.3 ms (reduction factor 2), and 2.6 ms (reduction factor 4).} \revbox{R2.1}

>>>>

\par A SPINS excitation k-space trajectory \cite{malik2012tailored} (Figure \ref{fig:Target}b) with 5 mm max resolution was used for the designs. 
The SPINS trajectory comprised three segments with radii ranging between 1-0.625, 0.625-0.375, and 0.375-0 cycles/cm, respectively.
The number of polar and azimuthal rotations were 15.5/2.125, 20.66/2.833, 15.5/2.125 for each segment, respectively.
The SPINS trajectories were first designed analytically and the final gradient waveforms and excitation k-space trajectories were designed from them 
using the minimum-time gradient waveform design method \cite{lustig2008fast}, 
for a 10 {\textmu}s dwell time and subject to the scanner's gradient amplitude and slew rate constraints of 200 mT/m and 700 T/m/s, respectively (Figure \ref{fig:Target}c). 
The durations of the three segments after minimum-time gradient design were 4.174, 4.326, and 1.5 ms, respectively.
With the exception of the simulations across undersampling factors, 
all pulse designs used this 10 ms trajectory.
With this trajectory and the 64$\times$64$\times$48 design grid size, 
the dimensions of the $\bm{W}$ matrix were 25,008 RF pulse samples, 
by 196,608 target k-space locations.

@@

\subsection*{k-Space Algorithm Parameters}
To evaluate how accuracy and compute time depend on k-space-domain design parameters and parallelization,
pulse designs were done across numbers of threads (i.e., how many patches were solved simultaneously; 1 to 32), 
patch widths (1 to 16 cycles/FOV), and inclusion widths (2 to 8 cycles/FOV). 
The number of threads were varied while holding the patch width and inclusion width both at 4 cycles/FOV.
The patch width was varied while holding the number of threads at 16, and the inclusion width at 4 cycles/FOV,
and the inclusion width was varied (2, 4, 6, and 8 cycles/FOV) while holding the number of threads at 16, and the patch width at 4 cycles/FOV. 
The sizes of the $\bm{W}$ matrices were also recorded, holding patch width constant at 4 cycles/FOV and varying the inclusion width.

\subsection*{L-Curves}
To compare the tradeoff between excitation error (measured by root-mean-square error)
and integrated RF root-mean-square (RMS) amplitude for spatial and k-space domain designs,
pulse designs were repeated while varying Tikhonov regularization parameters ($\lambda$ in Equation \ref{eq:Solution}) 
over five orders of magnitude. 
The k-space domain designs were repeated four times to investigate the two main sources of error:
finite patch and inclusion widths, 
and $B_1^+$ map product interpolation when building the $\bm{S}^H\bm{S}$ matrices. 
Specifically, for each $\lambda$ a design was performed using patch and inclusion widths of four (`Patch/Inclusion Widths = 4')
with interpolated $B_1^+$ map products (`Interpolated Matrices'),
patch and inclusion widths covering the entire design grid (`Patch/Inclusion Widths = $\infty$') with interpolated $B_1^+$ map products,
patch and inclusion widths of four without $B_1^+$ map product interpolation (`Exact Matrices'; 
$B_1^+$ maps were phase-modulated to each trajectory location before Fourier transform),
and patch and inclusion widths covering the entire design grid without $B_1^+$ map product interpolation. 
Note that the last case is equivalent to the original k-space domain method of Ref. \cite{Katscher:2003:Magn-Reson-Med:12509830}.
For each design, flip angle RMSE (calculated using the spatial domain non-uniform discrete Fourier transforms) and root-mean-square RF amplitude were
recorded.

@@

\subsection*{Excitation k-Space Undersampling}
An important application of parallel transmission is the reduction of multidimensional pulse durations by excitation k-space undersampling.
\textcolor{blue}{To compare the spatial domain and k-space domain methods across undersampling factors,
the number of polar and azimuthal rotations in each segment of the SPINS trajectory were increased and reduced relative to the reference design described above, 
by factors of 0.5, 2, and 4. 
That is, for a reduction factor of 0.5, the number of polar and azimuthal rotations in the trajectory were doubled for each of the three segments,
and they were halved for a reduction factor of 2.
This yielded pulse durations of 20.7 ms (reduction factor 0.5), 5.2 ms (reduction factor 2), and 2.7 ms (reduction factor 4).} \revbox{R2.1}

### 2020-10-23 Manuscript_r2/Result.tex
update text with dwell 10

Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for the reference spatial and k-space domain designs. 
Both designs were performed with 16 parallel threads and the 64$\times$64$\times$48 grid size (3 mm isotropic resolution), 
and the excitation patterns were evaluated against the target pattern on a 128$\times$128$\times$96 grid size (1.5 mm iso-resolution). 
The k-space domain design used patch and inclusion widths of 4.
The calculated root-mean-squared errors (RMSEs) were 2.42\% (spatial domain) and 2.68\% (k-space domain), 
respectively. 
For both design methods, most of the errors appeared at the edges of the transition band, 
and errors elsewhere were lower than 5\% of the target flip angle. 
This indicates uniform inner volume excitation while maintaining the outer volume intact. 
The parallelized k-space domain design required 2.9 seconds computation versus 31.8 seconds for the spatial domain method, a 91\% decrease.

@@

\par Figure \ref{fig:ComputationTime}c plots mean computation time and RMSE with different inclusion widths. 
The solid lines and dashed lines were obtained with patch widths of 4 and 8 cycles/FOV, respectively. 
Computation time increased and error decreased with increasing inclusion width,
since more excitation trajectory points were included in each target location's calculation for increasing inclusion width,
corresponding to an increased $\bm{S}^H\bm{S}$ matrix size. 
The RMSE was only slightly lower for a patch width of 8 versus 4 cycles/FOV, 
but the computation time was much higher for 8 cycles/FOV, across all inclusion widths. 
The knees in the curves occurred approximately at an inclusion width of 4 cycles/FOV,
so this value was used in subsequent designs.

\par Table \ref{fig:wsize} lists the size of the final matrix $\bm{W}$ in gigabytes,
versus inclusion width.
As inclusion width increases, more excitation trajectory points are used in the solution of the weights for each target location,
until the entire trajectory is used for each location (inclusion width = $\infty$ in the table),
corresponding to a full solution. 
With the inclusion width of 4 cycles/FOV used here, 
the matrix size was 98\% smaller than that of a full solution.

\subsection*{L-Curves}
Figure \ref{fig:LCurves} plots flip angle RMSE versus RF RMS amplitude for the spatial domain method
and different configurations of the k-space domain method.
The spatial domain method achieves the best overall tradeoff between error and RMS amplitude (dashed black curve),
which is matched by the k-space domain method when all target locations are solved simultaneously with
all excitation trajectory points included and exact $\bm{S}^H\bm{S}$ matrix construction (orange curve). 
When the inclusion and patch widths are limited to 4 cycles/FOV but the $\bm{S}^H\bm{S}$ 
matrices are still constructed exactly, there is an increase in error and RMS amplitude (solid blue curve). 
However, a larger penalty is incurred by interpolating the entries of the $\bm{S}^H\bm{S}$ matrices (dashed orange curve)
than by limiting the inclusion and patch widths.
Combining interpolation of the $\bm{S}^H\bm{S}$ matrix entries and patch and inclusion widths of 4 cycles/FOV yield 
the dashed blue curve, which has a higher error and RF amplitude than when interpolation or small patch and inclusion widths are
used alone.
Overall, these results and the results in Figure \ref{fig:ComputationTime} and Table \ref{fig:wsize}
show that the k-space domain method allows a tradeoff between computation time and memory usage versus
excitation error and RMS RF amplitude.
The dots on the spatial domain and k-space domain curves indicate the knees \textcolor{blue}{of}\revbox{R1.9} the curves corresponding to
the $\lambda$ values used for the designs in Figures \ref{fig:ErrorMap}, \ref{fig:ComputationTime}, \ref{fig:kspace_PTX_Acceleration}, and \ref{fig:kspace_PTX_B0}.
Note that the RMSE's in Figure \ref{fig:LCurves} are slightly lower for the spatial domain designs
and slightly higher for the k-space domain designs compared to other figures,
because the flip angle errors in Figure \ref{fig:LCurves} were calculated using 
spatial domain non-uniform fast Fourier transforms instead of Bloch equation simulations, 
to provide a more direct measure of the design error.

\subsection*{Gibbs Ringing}
Figure \ref{fig:GibbsRing}a shows slices of the excitation error pattern produced by pulses designed by the spatial domain method
on a 32$\times$32$\times$24 grid, which were Bloch-simulated on the original 128$\times$128$\times$96 grid. 
There is significant Gibbs ringing in the pattern (indicated by the red arrows),
and the pulses incur a higher RMSE (4.64\%) than pulses designed using either the spatial domain method with a finer 64$\times$64$\times$48 grid
(2.66\%; Figure \ref{fig:GibbsRing}b) or the k-space domain method with a 32$\times$32$\times$24 grid (3.00\%; Figure \ref{fig:GibbsRing}c). 
Gibbs ringing is not apparent in either the 64$\times$64$\times$48 spatial domain error pattern or the 32$\times$32$\times$24 k-space domain error pattern. 
The RMS RF amplitudes of the low resolution designs were both 0.005. 
Note that the error of the 64$\times$64$\times$48 spatial domain design is slightly higher than designs presented in other figures
due to the lower-resolution excitation trajectory. 
From a spatial domain point of view, 
the Gibbs ringing in the low-resolution spatial domain design was caused by the design's inability to observe and limit the ringing in the low-resolution design grid. 
From a k-space domain point of view, the Gibbs ringing in 
Figure \ref{fig:GibbsRing}a was due to implicit circulant end conditions at the edges of excitation k-space in the low-resolution
spatial domain design,
which led RF samples at one edge of k-space to wrap-around and affect target locations at the opposite edge of k-space. 
This effect is mitigated using a high-resolution spatial domain design grid, as illustrated in Figure \ref{fig:GibbsRing}b. 
However, even for a low-resolution k-space domain design there is no wrap-around effect in excitation k-space 
because the trajectory points that are incorporated in the weights solution for each patch of target locations are explicitly specified to be those in the immediate vicinity of 
the target points, without circulant end conditions. 
%Particularly, for the instance problems whose patches are at the edges of the k-space FOV, the excitation trajectory points at the other ends of the k-space FOV will not be incorporated into the design.

@@

\subsection*{Excitation k-Space Undersampling}
Figure \ref{fig:kspace_PTX_Acceleration} compares excitation error patterns produced by spatial domain-designed pulses (top row)
and k-space domain-designed pulses (middle row),
for different trajectory reduction factors which resulted in the SPINS trajectories plotted in the third row. 
For each design the k-space domain-designed pulses had higher error, 
but error increased smoothly with increasing reduction factor, 
as it did for the spatial domain designs.

>>>>

Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for the reference spatial and k-space domain designs. 
Both designs were performed with 16 parallel threads and the 64$\times$64$\times$48 grid size (3 mm isotropic resolution), 
and the excitation patterns were evaluated against the target pattern on a 128$\times$128$\times$96 grid size (1.5 mm iso-resolution). 
The k-space domain design used patch and inclusion widths of 4.
The calculated root-mean-squared errors (RMSEs) were 2.13\% (spatial domain) and 2.31\% (k-space domain), 
respectively. 
For both design methods, most of the errors appeared at the edges of the transition band, 
and errors elsewhere were lower than 5\% of the target flip angle. 
This indicates uniform inner volume excitation while maintaining the outer volume intact. 
The parallelized k-space domain design required 6.7 seconds computation versus 30.3 seconds for the spatial domain method, a 78\% decrease.

@@

\par Figure \ref{fig:ComputationTime}c plots mean computation time and RMSE with different inclusion widths. 
Computation time increased and error decreased with increasing inclusion width,
since more excitation trajectory points were included in each target location's calculation for increasing inclusion width,
corresponding to an increased $\bm{S}^H\bm{S}$ matrix size. 
The knees in the curves occurred approximately at an inclusion width of 4 cycles/FOV,
so this value was used in subsequent designs.

\par Table \ref{fig:wsize} lists the size of the final matrix $\bm{W}$ in gigabytes,
versus inclusion width.
As inclusion width increases, more excitation trajectory points are used in the solution of the weights for each target location,
until the entire trajectory is used for each location (inclusion width = $\infty$ in the table),
corresponding to a full solution. 
With the inclusion width of 4 cycles/FOV used here, 
the matrix size was 99\% smaller than that of a full solution.

\subsection*{L-Curves}
Figure \ref{fig:LCurves} plots flip angle RMSE versus RF RMS amplitude for the spatial domain method
and different configurations of the k-space domain method.
The spatial domain method achieves the best overall tradeoff between error and RMS amplitude (dashed black curve),
which is matched by the k-space domain method when all target locations are solved simultaneously with
all excitation trajectory points included and exact $\bm{S}^H\bm{S}$ matrix construction (solid orange curve). 
When the inclusion and patch widths are limited to 4 cycles/FOV but the $\bm{S}^H\bm{S}$ 
matrices are still constructed exactly, there is an increase in error and RMS amplitude (solid blue curve). 
However, a larger penalty is incurred by interpolating the entries of the $\bm{S}^H\bm{S}$ matrices (dashed orange curve)
than by limiting the inclusion and patch widths.
Combining interpolation of the $\bm{S}^H\bm{S}$ matrix entries and patch and inclusion widths of 4 cycles/FOV yield 
the dashed blue curve, which has a higher error and RF amplitude than when interpolation or small patch and inclusion widths are
used alone.
Overall, these results and the results in Figure \ref{fig:ComputationTime} and Table \ref{fig:wsize}
show that the k-space domain method allows a tradeoff between computation time and memory usage versus
excitation error and RMS RF amplitude.
The dots on the spatial domain and k-space domain curves indicate the knees \textcolor{blue}{of}\revbox{R1.9} the curves corresponding to
the $\lambda$ values used for the designs in Figures \ref{fig:ErrorMap}, \ref{fig:ComputationTime}, \ref{fig:kspace_PTX_Acceleration}, and \ref{fig:kspace_PTX_B0}.
Note that the RMSE's in Figure \ref{fig:LCurves} are slightly lower for the spatial domain designs
and slightly higher for the k-space domain designs compared to other figures,
because the flip angle errors in Figure \ref{fig:LCurves} were calculated using 
spatial domain non-uniform discrete Fourier transforms instead of Bloch equation simulations, 
to provide a more direct measure of the design error.

\subsection*{Gibbs Ringing}
Figure \ref{fig:GibbsRing}a shows slices of the excitation error pattern produced by pulses designed by the spatial domain method
on a 32$\times$32$\times$24 grid, which were Bloch-simulated on the original 128$\times$128$\times$96 grid. 
There is significant Gibbs ringing in the pattern (indicated by the red arrows),
and the pulses incur a higher RMSE (4.90\%) than pulses designed using either the spatial domain method with a finer 64$\times$64$\times$48 grid
(2.43\%; Figure \ref{fig:GibbsRing}b) or the k-space domain method with a 32$\times$32$\times$24 grid (2.96\%; Figure \ref{fig:GibbsRing}c). 
Gibbs ringing is not apparent in either the 64$\times$64$\times$48 spatial domain error pattern or the 32$\times$32$\times$24 k-space domain error pattern. 
The RMS RF amplitudes of the low resolution designs were both 0.004. 
Note that the error of the 64$\times$64$\times$48 spatial domain design is slightly higher than designs presented in other figures
due to the lower-resolution excitation trajectory. 
From a spatial domain point of view, 
the Gibbs ringing in the low-resolution spatial domain design was caused by the design's inability to observe and limit the ringing in the low-resolution design grid. 
From a k-space domain point of view, the Gibbs ringing was due to implicit circulant end conditions at the edges of excitation k-space,
which led RF samples at one edge of k-space to wrap-around and affect target locations at the opposite edge of k-space. 
This effect is mitigated using a high-resolution spatial domain design grid, as illustrated in Figure \ref{fig:GibbsRing}b. 
However, even for a low-resolution k-space domain design there is no wrap-around effect in excitation k-space 
because the trajectory points that are incorporated in solution for each patch are explicitly specified to be those in the immediate vicinity of 
that patch, without circulant end conditions. 
%Particularly, for the instance problems whose patches are at the edges of the k-space FOV, the excitation trajectory points at the other ends of the k-space FOV will not be incorporated into the design.

@@

\subsection*{Excitation k-Space Undersampling}
Figure \ref{fig:kspace_PTX_Acceleration} compares excitation error patterns produced by spatial domain-designed pulses (top row)
and k-space domain-designed pulses (middle row),
for different trajectory reduction factors which resulted in the SPINS trajectories plotted in the third row. 
For each design the k-space domain-designed pulses had higher error, 
but error increased smoothly with increasing reduction factor, 
as it did for the spatial domain designs. 
\textcolor{blue}{Figure \ref{fig:kspace_PTX_Acceleration} also reports mean computation time for each design.
The spatial domain times were fairly constant across reduction factors despite the decreasing number of time samples with increasing reduction factor.
This was because the size of the FFT operations in the NUFFTs 
depended not on the length of the trajectory but on the size of the target pattern which did not change with reduction factor,
and the FFT operations dominated the NUFFT computation times relative to the gridding operations. % for these three-dimensional problems,
Conversely, the k-space domain times did decrease with reduction factor since the number and sizes of the $\bm{S}^H\bm{S}$
matrices depend on the trajectory length.} \revbox{R2.1}

### 2020-10-23 Manuscript_r2/Theory.tex
update text with dwell 10

\par If all points on the excitation k-space trajectory are considered in Equation \ref{eq:ScalerForm},
then there is no reduction in computation compared to a conventional pseudoinverse-based pulse design.
However, because $B_1^+$ maps are localized near $\vec{k} = 0$ in excitation k-space,
only a small number ($\ll N_t$) of trajectory points near the target location $\vec{k}_j$ can contribute significantly
to the excitation pattern at $\vec{k}_j$ or its neighbors, 
and therefore need to be considered in the subproblem;
all other trajectory points can be ignored.
This means Equation \ref{eq:ScalerForm} can be modified to:
\begin{equation}
\delta(\vec{k}-\vec{k}_j) = \sum_{\vec{k}_i \in \mathbb{N}}\sum_{c=1}^{N_c} w_c(\vec{k}_i) s_c(\vec{k}-\vec{k}_i),
\end{equation} 
where $\mathbb{N}$ is the set of trajectory points in the vicinity of $\vec{k}_j$. 
In this work `inclusion width' is defined as the distance, 
in \textcolor{blue}{phase cycles over the excitation field-of-view (cycles/FOV), }\revbox{R1.2} 
from each target location $\vec{k}_j$ within which which all trajectory points are accrued into $\mathbb{N}$.
This reduced set of trajectory points reduces the column dimension of $\bm{S}$
and both dimensions of $\bm{S}^H\bm{S}$,
and implies that the design matrix $\bm{W}$ is sparse.
Figure \ref{fig:Patch}a illustrates a target point $\vec{k}_j$ for a two-dimensional pulse design, 
and the nearby points on the trajectory that need to be included in the solution for $\bm{w}_j$
for an inclusion width of 4 cycles/FOV.

@@

%\subsection*{Efficient construction of $\bm{S}^{H}\bm{S}$ matrix}
\par Constructing the $\bm{S}^{H}\bm{S}$ matrix by first constructing $\bm{S}$ is computationally expensive 
because it requires each channel's $B_1^+$ map to be shifted to each trajectory location $\vec{k}_i$
by phase modulation followed by Fourier transform, or by Fourier transform followed by interpolation. 
Furthermore, 
the matrix multiplication between $\bm{S}^{H}$ and $\bm{S}$ is also computationally intensive due to the potentially 
large row dimension of $\bm{S}$, if the zero excitation condition is enforced on a large grid of points around each $\vec{k}_j$.
The computational costs can be reduced by truncating the $B_1^+$ maps in k-space, 
but this introduces large errors. 
Instead, inspired by the non-Cartesian GRAPPA method of Ref \cite{luo2019grappa}, 
we propose to construct the Hermitian $\bm{S}^{H}\bm{S}$ matrix directly via interpolation of the Fourier transforms
of inner products of pairs of $B_1^+$ maps. 
The $\bm{S}^H\bm{S}$ matrix can be written in block form as:
\begin{equation}\label{eq:SHS_blocks}
\bm{S}^{H}\bm{S} = 
\begin{pmatrix}
\bm{S}_1^{H}\bm{S}_1 & \cdots & \bm{S}_1^{H}\bm{S}_{N_c} \\
\vdots  &  \ddots & \vdots  \\
\bm{S}_{N_c}^{H}\bm{S}_1 & \cdots & \bm{S}_{N_c}^{H}\bm{S}_{N_c} 
\end{pmatrix}, 
\end{equation}
where each sub-matrix $\bm{S}_i^H\bm{S}_j$ contains inner products of the Fourier transforms of channel $i$ and channel $j$'s 
$B_1^+$ maps, after they are shifted to be centered different points on the excitation trajectory corresponding to the row 
and column indices of the sub-matrix.
These inner products can be calculated by interpolating the Fourier transform of the inner product of 
channel $i$ and channel $j$'s $B_1^+$ maps. 
In other words, each element in the Hermitian matrix $\bm{S}_i^{H}\bm{S}_j$ 
is the vector sum of channel $i$ and channel $j$'s shifted k-space $B_1^+$ maps, 
which is also a single point of their k-space convolution. 
Via the multiplication property of the Fourier transform, 
this convolution in k-space can be calculated from the Fourier transform of the dot product of the two spatial domain $B_1^+$ maps. 
For further details, please refer to Ref. \cite{luo2019grappa}.
%In practice, $\bm{S}^{H}\bm{S}$ is constructed in the following way. 
%We first represent the $\bm{S}^{H}\bm{S}$ matrix with block matrices. Each block matrix $\bm{S}_i^{H}\bm{S}_j$ is of size $N_n$ by $N_n$, and $\bm{S}_i$ and $\bm{S}_j$ are the columns of $\bm{S}$ related to the k-space sensitivity maps of the $i$-th and $j$-th coils respectively.

>>>>

\par If all points on the excitation k-space trajectory are considered in Equation \ref{eq:ScalerForm},
then there is no reduction in computation compared to a conventional pseudoinverse-based pulse design.
However, because $B_1^+$ maps are localized near $\vec{k} = 0$ in excitation k-space,
only a small number ($\ll N_t$) of trajectory points near the target location $\vec{k}_j$ can contribute significantly
to the excitation pattern at $\vec{k}_j$ or its neighbors, 
and therefore need to be considered in the subproblem;
all other trajectory points can be ignored.
This means Equation \ref{eq:ScalerForm} can be modified to:
\begin{equation}
\delta(\vec{k}-\vec{k}_j) = \sum_{\vec{k}_i \in \mathbb{N}}\sum_{c=1}^{N_c} w_c(\vec{k}_i) s_c(\vec{k}-\vec{k}_i),
\end{equation} 
where $\mathbb{N}$ is the set of trajectory points in the vicinity of $\vec{k}_j$. 
In this work `inclusion width' is defined as the distance, 
in \textcolor{blue}{phase cycles over the excitation field-of-view (cycles/FOV), }\revbox{R1.2} 
from each target location $\vec{k}_j$ within which all trajectory points are accrued into $\mathbb{N}$.
This reduced set of trajectory points reduces the column dimension of $\bm{S}$
and both dimensions of $\bm{S}^H\bm{S}$,
and implies that the design matrix $\bm{W}$ is sparse.
Figure \ref{fig:Patch}a illustrates a target point $\vec{k}_j$ for a two-dimensional pulse design, 
and the nearby points on the trajectory that need to be included in the solution for $\bm{w}_j$
for an inclusion width of 4 cycles/FOV.

@@

%\subsection*{Efficient construction of $\bm{S}^{H}\bm{S}$ matrix}
\par Constructing the $\bm{S}^{H}\bm{S}$ matrix by first constructing $\bm{S}$ is computationally expensive 
because it requires each channel's $B_1^+$ map to be shifted to each trajectory location $\vec{k}_i$
by phase modulation followed by Fourier transform, or by Fourier transform followed by interpolation. 
Furthermore, 
the matrix multiplication between $\bm{S}^{H}$ and $\bm{S}$ is also computationally intensive due to the potentially 
large row dimension of $\bm{S}$, if the zero excitation condition is enforced on a large grid of points around each $\vec{k}_j$.
The computational costs can be reduced by truncating the $B_1^+$ maps in k-space, 
but this introduces large errors. 
Instead, inspired by the non-Cartesian GRAPPA method of Ref \cite{luo2019grappa}, 
we propose to construct the Hermitian $\bm{S}^{H}\bm{S}$ matrix directly via interpolation of the Fourier transforms
of inner products of pairs of $B_1^+$ maps. 
The $\bm{S}^H\bm{S}$ matrix can be written in block form as:
\begin{equation}\label{eq:SHS_blocks}
\bm{S}^{H}\bm{S} = 
\begin{pmatrix}
\bm{S}_1^{H}\bm{S}_1 & \cdots & \bm{S}_1^{H}\bm{S}_{N_c} \\
\vdots  &  \ddots & \vdots  \\
\bm{S}_{N_c}^{H}\bm{S}_1 & \cdots & \bm{S}_{N_c}^{H}\bm{S}_{N_c} 
\end{pmatrix}, 
\end{equation}
where each sub-matrix $\bm{S}_i^H\bm{S}_j$ contains inner products of the Fourier transforms of channel $i$ and channel $j$'s 
$B_1^+$ maps, after they are shifted to be centered different points on the excitation trajectory corresponding to the row 
and column indices of the sub-matrix.
These inner products can be calculated by interpolating the Fourier transform of the dot product of 
channel $i$ and channel $j$'s $B_1^+$ maps. 
In other words, each element in the Hermitian matrix $\bm{S}_i^{H}\bm{S}_j$ 
is the vector sum of channel $i$ and channel $j$'s shifted k-space $B_1^+$ maps, 
which is also a single point of their k-space convolution. 
Via the multiplication property of the Fourier transform, 
this convolution in k-space can be calculated from the Fourier transform of the dot product of the two spatial domain $B_1^+$ maps. 
For further details, please refer to Ref. \cite{luo2019grappa}.
%In practice, $\bm{S}^{H}\bm{S}$ is constructed in the following way. 
%We first represent the $\bm{S}^{H}\bm{S}$ matrix with block matrices. Each block matrix $\bm{S}_i^{H}\bm{S}_j$ is of size $N_n$ by $N_n$, and $\bm{S}_i$ and $\bm{S}_j$ are the columns of $\bm{S}$ related to the k-space sensitivity maps of the $i$-th and $j$-th coils respectively.
